Lens Modeling in \sw

### 2014-01-24 text/ms.tex
added bylines

\title{Lens Modeling in \sw}
\author{First Author,\altaffilmark{1}
Second Author,\altaffilmark{2} and
Third Author\altaffilmark{3}}
\altaffiltext{1}{First place}
\altaffiltext{2}{Second place}
\altaffiltext{3}{Third place}

>>>>

\title{Lens Modeling in \sw}
\author{Rafael Kueng,\altaffilmark{1}
Phil Marshall,\altaffilmark{2}
Anupreeta More,\altaffilmark{3}
Aprajita Verma,\altaffilmark{4}
Amit Kapadia,\altaffilmark{5}
Elisabeth Baeten,\altaffilmark{6}
Claude Cornen,\altaffilmark{6}
Christine McMillan,\altaffilmark{6}
Julianne Wilcox,\altaffilmark{6}
Jonas Odermatt,\altaffilmark{7}
Jonathan Coles,\altaffilmark{8}
Surhud More\altaffilmark{3}
and Prasenjit Saha\altaffilmark{1}
}
\altaffiltext{1}{Physik-Institut, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland}
\altaffiltext{2}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford University, 452 Lomita Mall, Stanford, CA 94035, USA}
\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa-shi 277-8583, Japan}
\altaffiltext{4}{Oxford Astrophysics, Keble Road, Oxford OX1 3RH, UK}
\altaffiltext{5}{Adler Planetarium, 1300 S. Lake Shore Drive,
  Chicago, IL 60605, USA}
\altaffiltext{6}{Spacewarps}
\altaffiltext{7}{Kantonsschule Zug, L\"ussiweg 24, 6300 Zug, Switzerland}
\altaffiltext{8}{Exascale
  Research Computing Lab, Versailles Saint-Quentin-en-Yvelines
  University, 55 Avenue des Etats Unis, 78000, Versailles, France}
